---
title: "Violin plots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Violin plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  fig.width = 7,
  fig.height = 5
)
```
```{r load}
library(ercantools)
data(example_peaks)
```

## Overview

The violin functions compare binding distributions between chromosomes.
Four functions cover the main use cases:

| Function | Y-axis | Groups |
|---|---|---|
| `violin_log2FC()` | log2FC | chrX vs pooled autosomes |
| `violin_counts()` | Normalized counts | chrX vs autosomes, 2 conditions |
| `violin_log2FC_all_chr()` | log2FC | Each chromosome separately |
| `violin_counts_all_chr()` | Normalized counts | Each chromosome x 2 conditions |

## `violin_log2FC()`

Compares chrX peaks against all autosomes pooled. A Welch t-test
p-value is annotated automatically.
```{r violin_log2FC}
violin_log2FC(
  object          = example_peaks,
  title           = "log2FC: chrX vs autosomes",
  ylab            = "log2(Fold Change)",
  chr_of_interest = "chrX",
  ylim            = c(-3, 3),
  pvalue_y_position = 2.5
)
```

## `violin_counts()`

Shows four groups: baseline-A, baseline-X, condition-A, condition-X.
```{r violin_counts}
violin_counts(
  object           = example_peaks,
  title            = "Normalized counts: chrX vs autosomes",
  conc_condition   = "Conc_degron",
  condition_name   = "degron",
  conc_baseline    = "Conc_notag",
  baseline_name    = "notag",
  ylim             = c(0, 16),
  label.y_plot     = c(13, 14, 15, 16)
)
```

## `violin_log2FC_all_chr()`

One violin per chromosome with significance brackets vs chrX.
```{r violin_log2FC_all_chr, fig.width = 9}
violin_log2FC_all_chr(
  object          = example_peaks,
  title           = "log2FC per chromosome",
  ylab            = "log2(Fold Change)",
  chr_of_interest = "chrX",
  ylim            = c(-3, 3)
)
```

## `violin_counts_all_chr()`

Two paired violins per chromosome separated by condition.
```{r violin_counts_all_chr, fig.width = 11}
violin_counts_all_chr(
  object           = example_peaks,
  title            = "Normalized counts per chromosome",
  conc_condition   = "Conc_degron",
  condition_name   = "degron",
  conc_baseline    = "Conc_notag",
  baseline_name    = "notag",
  ylim             = c(0, 16)
)
```
